MS_CNuptake.Rmd

### 2022-10-12 MS_CNuptake.Rmd
change map style

plot_grid(a3,a4,a5,a6,a7,a8,
          a9,a10,a11,a12,a13,a14,
          nrow=2,
          rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
          labels = c('(a)',' ','(b)',' ','(c)',' ',
                     '(d)',' ','(e)',' ','(f)',' '))

#this is for showing points
ggsave(paste("./output/newphy_figs5.jpg",sep=""),width = 20, height = 10*(2/3))
```

@@

plot_grid(a3,a4,a5,a6,a7,a8,
          a9,a10,a11,a12,a13,a14,
          nrow=2,
          rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
          labels = c('(a)',' ','(b)',' ','(c)',' ',
                     '(d)',' ','(e)',' ','(f)',' '))
ggsave(paste("./output/newphy_fig2.jpg",sep=""),width = 20, height = 10*(2/3))
```

>>>>

plot_grid(a3,a4,a5,a6,
          a7,a8,a9,a10,
          a11,a12,a13,a14,
          nrow=3,
          rel_widths = c(4.5/12, 1.5/12,4.5/12,1.5/12),
          labels = c('(a)',' ','(b)',' ',
                     '(c)',' ','(d)',' ',
                     '(e)',' ','(f)',' '))

#this is for showing points
ggsave(paste("./output/newphy_figs5.jpg",sep=""),width = 16, height = 12)

@@

plot_grid(a3,a4,a5,a6,
          a7,a8,a9,a10,
          a11,a12,a13,a14,
          nrow=3,
          rel_widths = c(4.5/12, 1.5/12,4.5/12,1.5/12),
          labels = c('(a)',' ','(b)',' ',
                     '(c)',' ','(d)',' ',
                     '(e)',' ','(f)',' '))
ggsave(paste("./output/newphy_fig2.jpg",sep=""),width = 16, height = 12)
